Ideal model selection is impossible

### 2014-10-31 Facticity/Facticity/paper.tex
lemma aant fixen

\begin{definition}
We call $\phi_1, \phi_2, \ldots$ a \emph{partial computable numbering} of some subset of the partial computable functions, if there exists a partial computable function $u: \N \times \B \to \B \cup \infty$ such that $u(i, p) = \phi_i(p)$. We call $u$ the universal model for the numbering. We call a numbering \emph{optimal} if there is a constant $c$ such that for all $i$, we have $|i| \leq K(\phi_i) + c$.
\end{definition}

\begin{lemma}
There exists an acceptable, optimal partial computable numbering of the partial computable functions.
\label{lemma:optimal-numbering}
\end{lemma}
\begin{proof}
Let $\psi_1, \psi_2, \ldots$ be some acceptable numbering, with some $\psi_{\text{div}}$ with is undefined for all its arguments. Let 
\begin{align*}
	\phi_{\bar\imath p} &= \psi_{\psi_i(p)} \qquad\text{if $\psi_i(p)$ is defined}\\
	\phi_{\bar\imath p} &= \psi_{\text{div}} \qquad\text{otherwise}\\
	\phi_{j} &= \psi_{\text{div}} \qquad\text{if $j$ can not be read as $\bar\imath p$}
\end{align*}

\noindent To show that this numbering is acceptable. We must provide two computable function to translate t and from a given acceptable numbering. We use $\psi$ for this purpose. To find a $\phi_j$ which corresponds to a given $\psi_i$, we can simply use the identity function $\psi_d(x) = x$. For a given $\psi_i$, the function $\phi_{\overline{d}i}$ computes the same function.

@@

\begin{lemma}
  Let $\M$ be any model class and let $\M'\subseteq \M$ be a sub-model with the following properties:
\begin{enumerate}
  \item There exists an optimal partial computable numbering $\eta_1, \eta_2, \ldots$ for $M'$,
  \item $L^{\M'}(x)-L^{\M}(x)\le c$ for some constant $c$, all $x$.
\end{enumerate}
There is an enumeration $\phi_1,\phi_2,\ldots$ of $\M$, such that $S^\phi_{\M}(x) = S^\eta_{\M'}(x)+1$ for all $x$.
\end{lemma}
\begin{proof}
Let $\psi_1, \psi_2, \ldots$ be some acceptable numbering. Let $u$ be the universal model for the numbering $\eta_1, \eta_2, \ldots$. We define the numbering $\phi$ as follows:
\begin{align}
\phi_{0}i(p) &= u(i, p) \\
\phi1^r0i(p) &= \psi_i(p) \\
\phi_j(\cdot) &= \infty \quad\text{if $j$ contains no zeroes.}
\end{align}
Note that with this definition, we have $K^\phi(f) \leq K^\eta(f) \leq K^\psi(f) + c$ if $f \in \M'$. If $f$ is not in $\M'$, we have $K^\phi(f) = K^\psi(f) + r + 1 - c'$, by the same argument as used in the proof of Lemma~\ref{lemma:building-block}.

>>>>

\begin{definition}
We call a numbering $\eta_1,\eta_2,\ldots$ \emph{optimal} if there is a constant $c$ such that for all $i$, we have $\min\{|j|:\eta_i=\eta_j\} \leq K(\eta_i) + c$.
\end{definition}

\begin{lemma}
There exists an acceptable, optimal numbering of the partial computable functions.
\label{lemma:optimal-numbering}
\end{lemma}
\begin{proof}
Let $\psi_1, \psi_2, \ldots$ be some acceptable numbering, with some $\psi_{\text{div}}$ with is undefined for all its arguments. Let 
\[\begin{cases}
	\phi_{j} = \psi_{\text{div}} &\text{if $j$ can not be read as $\bar\imath p$}\\
	\phi_{\bar\imath p} = \psi_{\psi_i(p)} &\text{if $\psi_i(p)$ is defined}\\
	\phi_{\bar\imath p} = \psi_{\text{div}} & \text{otherwise}
\end{cases}\]

\noindent To show that this numbering is acceptable, we must provide two computable functions to translate to and from a given acceptable numbering. We use $\psi$ for this purpose. To find a $\phi_j$ which corresponds to a given $\psi_i$, we can simply use the identity function $\psi_d(x) = x$. For a given $\psi_i$, the function $\phi_{\overline{d}i}$ computes the same function.

@@

\begin{lemma}
  Let $\psi_1,\psi_2,\ldots$ be any acceptable enumeration of the partial recursive functions.
  Let $\M$ be any model class and let $D:\{0,1\}^*\to\N$ be a computable decoding function with a prefix-free domain that maps function descriptions to their indices in $\psi$, i.e. if $f=\psi_{D(p)}$ then $p$ is a $D$-description of $f$. Let $\M'=\{\psi_i:i\in\tn{range}(D)\}$. Further assume there is a constant $c$ such that
\begin{enumerate}
  \item $\forall_{f\in\M'}:\min\{|p|:\psi_{D(p)}=f\}\le K^\psi(f)+c$
  \item $\forall_x:L^{\M'}(x)-L^{\M}(x)\le c$.
\end{enumerate}
Then is an enumeration $\phi_1,\phi_2,\ldots$ of the partial recursive functions such that $S^\phi_{\M}(x) = 1$ for all $x$.
\end{lemma}
\begin{proof}
We define the numbering $\phi$ as follows:
\[\begin{cases}
\phi_0(p) = 1^r 0 D(p) \\
\phi_{1^r0i}(p) = \psi_i(p) \\
\phi_j(\cdot) = \infty &\text{if $j$ contains no zeroes.}
\end{cases}\]
First suppose $f\in\M'$. Then
\[\begin{split}
K^\phi(f)&=\min\{K^\phi(i):\phi_i=f\}\\
&=\min\{|\bar\jmath q|:\phi_j(q)=i, \phi_i=f\}\\
&=\min\{|\bar\jmath q|:\phi_{\phi_j(q)}=f\}\\
&\le\min\{|\bar0 q|:\phi_{\phi_0(q)}=f\}~\text{(using $j=0$)}\\
&=\min\{|\bar0 q|:\phi_{1^r0 D(q)}=f\}\\
&=|\bar 0|+\min\{|q|:\psi_{D(q)}=f\}\\
&\le K^\psi(f)+c+|\bar 0|,
\end{split}
\]
where the last inequality uses the first assumption.

\hrule

Note that with this definition, we have $K^\phi(f) \leq K^\eta(f) \leq K^\psi(f) + c$ if $f \in \M'$. If $f$ is not in $\M'$, we have $K^\phi(f) = K^\psi(f) + r + 1 - c'$, by the same argument as used in the proof of Lemma~\ref{lemma:building-block}.
